\documentclass[13pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{enumerate}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{plotmarks}
\usepackage{amssymb}
\usepackage{xcolor}

\usepackage{verbatim}
%\usepackage{enumitem}
\usepackage{listings}

\renewcommand{\thesection}{\arabic{section}}
\renewcommand\theparagraph{\thesubsubsubsection.\arabic{paragraph}} % optional; useful if paragraphs are to be numbered


\begin{document}
	
\begin{titlepage}
	\centering
	\vspace{2cm}
	{\huge\bfseries Report of Project of Semester S1: Nonparametric method for image analysis \par}
	\vspace{2cm}
	{\Large\itshape Students:\\
		Loc Thi Thuy Linh\\
		Nguyen Duc Tho\par}
	\vfill
	supervised by\par
	\large Nghiem Thi Phuong \& Tran Giang Son\\
	ICT Department, USTH\par
	\vfill
% Bottom of the page
	{\large \today\par}
\end{titlepage}

\tableofcontents{}
\newpage

\section{Introduction}

\subsection{What is clustering?}

\subsection{Why is clustering used?}

\subsection{How does clustering work?}

\subsection{Clustering categories}
\begin{enumerate}[a.]
	\item Parametric
	\item Non-parametric
\end{enumerate}

\section{K-means}

\subsection{What?}

\subsection{Why?}

\subsection{How?}

\subsection{Advantages and disadvantages}
%lead to the next part


\section{Non-parametric: Meanshift}

\subsection{What?}

Mean shift  is a popular non-parametric clustering algorithm based on the
idea of associating each data point to a mode of the underlying probability density
function\textsuperscript{2.1}.{\linebreak}

Assuming that we have a dataset of students and corresponding mark for each of them 
in final exam as the table below. How do we categorize these students into groups base on their marks?
\begin{center}
 \begin{tabular}{||c c c||} 
 \hline
 No & Student & Mark \\ [0.5ex] 
 \hline\hline
 1 & S1 & 5.0 \\ 
 \hline
 2 & S2 & 4.0 \\
 \hline
 3 & S3 & 4.5 \\
 \hline
 4 & S4 & 5.7 \\
 \hline
 5 & S5 & 6.0 \\ 
  \hline
 6 & S6 & 9.0 \\ 
  \hline
 7 & S7 & 8.7 \\ 
  \hline
 8 & S8 & 9.5 \\ 
 [1ex] 
 \hline
\end{tabular}
\end{center}

Meanshift is a powerful tool for us in this case although the idea behind it is very simple.
Imagine that the set of marks was sampled from a probability distribution. Meanshift seeks for modes of  the underlying distribution for this set of marks. Number of modes corresponds to the number of groups of students.
\pgfplotsset{grid style={dashed,gray}}
\pgfplotsset{minor grid style={dashed,red}}
\pgfplotsset{major grid style={dotted,green!50!black}}

%Probability plot
\begin{tikzpicture}
	\begin{axis}[
	axis lines=left,
	xtick={0,1,...,10},ytick = {0,0.2,...,1},
	grid=both,
	xlabel = {Mark},
	ylabel = {Probability}
	]
		%First Mode
		\addplot [
		domain=3:7,
		samples=100,
		color=red,
		]
		{-0.125*x^2 + 1.25*x - 2.625};
		
		\addplot [
		 domain=0:3,
		 samples=10, 
		 color=red,
		 ]
		 {0.002};
		 \addplot [
		 domain=7:8,
		 samples=10, 
		 color=red,
		 ]
		 {0.002};
		 \addplot [
		 domain=10:11,
		 samples=10, 
		 color=red,
		 ]
		 {0.002};
		 \addplot [
		domain=0:12, 
		samples=2,
		color = white
		]
		{1};
		%Second mode
		\addplot [
		domain=8:10, 
		samples=100, 
		color=red,
		]
		{-0.2*x^2 + 3.6*x - 16};
		 
		 %First Mode
		
		\draw[red,fill,thick] (50,50) circle (0.05cm);
		\node[black,above] at (axis cs:5,0.5){\small{Mode 1}};
		 %S1
		\draw[red,thick] (50,4) circle (0.2cm);
		\node[red,above] at (axis cs:5,0.1){\small{S1}};
		 %S2
		\draw[blue,thick] (40,4) circle (0.2cm);
		\node[blue,left] at (axis cs:4,0.08){\small{S2}};
		 %S3
		\draw[blue,thick] (45,4) circle (0.2cm);
		\node[blue,above] at (axis cs:4.5,0.06){\small{S3}};
		 %S4
		\draw[blue,thick] (57,4) circle (0.2cm);
		\node[blue,above] at (axis cs:5.7,0.06){\small{S4}};
		 %S5
		\draw[blue,thick] (60,4) circle (0.2cm);
		\node[blue,right] at (axis cs:6,0.08){\small{S5}};
		
		 %Second Mode
		 
		 \draw[red,fill,thick] (90,20) circle (0.05cm);
		 \node[black,above] at (axis cs:9,0.2){\small{Mode 2}};
		 %S6
		\draw[red,thick] (90,4) circle (0.2cm);
		\node[red,above] at (axis cs:9,0.1){\small{S6}};
		 %S7
		\draw[blue,thick] (87,4) circle (0.2cm);
		\node[blue,left] at (axis cs:8.7,0.08){\small{S7}};
		 %S8
		\draw[blue,thick] (95,4) circle (0.2cm);
		\node[blue,right] at (axis cs:9.5,0.08){\small{S8}};
		
		%Legend
		\addlegendentry{Probability Distribution Function}
	\end{axis}
\end{tikzpicture}

As can be seen from the graph above, we have two groups of students correspond to two modes of probability distribution function

\subsection{Why?}

\subsection{How?}

\subsection{Advantages and disadvantages}

\section{Evaluation}

\begin{enumerate}[(a) ]
\item What is evaluation? Convergence(performance) | accuracy | Complexity
\item Dataset (name, source, type, image size ....)
\item Computer test configuration
\item Program language
\item Results (time | number of cluster | accuracy) ~~~> describe detail.
\item Comparison of the two methods
\end{enumerate}
	
	
\section{Conclusion}
\section{Reference}
[2.1] http://vision.cs.ucla.edu/papers/vedaldiS08quick.pdf
\end{document}